Titeln på avhandlingens språk

### 2022-12-15 background.tex
modifications to work with thesis

\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{figs/task.png}
        \caption{%
            Overview of a task in a \ac{WCA}, composed of a series of steps.
            Each steps starts with an instruction being provided to the user and ends with the instruction for the next step.
            The \ac{WCA} continuously samples the task state, automatically triggering transitions between steps as correct (or incorrect) states are recognized.
        }\label{fig:task}
    \end{subfigure}\\
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{figs/step_time.png}
        \caption{%
            Breakdown of a step into its timing components.
            The instruction for step \( M \) and \( M + 1 \) are provided to the user at \( t_0 \) and \( t_{n+1} \), respectively.
            \( t_k | k \in \{1, \ldots, n \} \) correspond to the \ac{WCA} sampling instants for step \( M \), and \( t_c \) marks the instant at which the user finishes performing the instruction.
        }\label{fig:step}
    \end{subfigure}
    \caption{Key concepts in \acl{WCA}}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figs/new_model/mu_fits_exgaussian_slice0.png}
    \caption{%
        \( \mu \) parameter of \acs*{exGaussian} distributions fitted to execution times of the first four steps of segments of steps subject to the same \ac{TTF} in~\cite{olguinmunoz:impact2021}.
        Distributions were fitted using \ac{MLE}.
    }\label{fig:muexgaussian}
\end{figure}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figs/new_model/dist_fits_neuro.png}
    \caption{%
        Example \ac{exGaussian} fits on execution times from steps \numrange{4}{8} in a segment of steps at the maximum experimental \ac{TTF}.
        The effects of neuroticism are clearly visible in the tail and the mean of the distributions.
    }\label{fig:fitsneuro}
\end{figure*}

>>>>

\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{publications/2023EdgeDroid2/figs/task.png}
        \caption{%
            Overview of a task in a \ac{WCA}, composed of a series of steps.
            Each steps starts with an instruction being provided to the user and ends with the instruction for the next step.
            The \ac{WCA} continuously samples the task state, automatically triggering transitions between steps as correct (or incorrect) states are recognized.
        }\label{fig:task}
    \end{subfigure}\\
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{publications/2023EdgeDroid2/figs/step_time.png}
        \caption{%
            Breakdown of a step into its timing components.
            The instruction for step \( M \) and \( M + 1 \) are provided to the user at \( t_0 \) and \( t_{n+1} \), respectively.
            \( t_k | k \in \{1, \ldots, n \} \) correspond to the \ac{WCA} sampling instants for step \( M \), and \( t_c \) marks the instant at which the user finishes performing the instruction.
        }\label{fig:step}
    \end{subfigure}
    \caption{Key concepts in \acl{WCA}}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{publications/2023EdgeDroid2/figs/new_model/mu_fits_exgaussian_slice0.png}
    \caption{%
        \( \mu \) parameter of \acs*{exGaussian} distributions fitted to execution times of the first four steps of segments of steps subject to the same \ac{TTF} in~\cite{olguinmunoz:impact2021}.
        Distributions were fitted using \ac{MLE}.
    }\label{fig:muexgaussian}
\end{figure}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{publications/2023EdgeDroid2/figs/new_model/dist_fits_neuro.png}
    \caption{%
        Example \ac{exGaussian} fits on execution times from steps \numrange{4}{8} in a segment of steps at the maximum experimental \ac{TTF}.
        The effects of neuroticism are clearly visible in the tail and the mean of the distributions.
    }\label{fig:fitsneuro}
\end{figure*}

### 2022-12-15 implications_footprint.tex
modifications to work with thesis

\begin{figure}
    \centering
    \begin{subfigure}[]{\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/new_model/lifetime_all_ttfs.png}
        \caption{%
            Evolution of mean application lifetimes as \acp{TTF} increase.
            Error bars indicate \SI{95}{\percent} \acp{CI}.
        }
    \end{subfigure}
    \begin{subfigure}[]{\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/new_model/lifetime_diff.png}
        \caption{%
            Percentage difference in mean application lifetimes with respect to the reference model at select \acp{TTF}.
            Error bars indicate the \SI{95}{\percent} \acp{CI}, calculated using a two-sided T-test.
        }
    \end{subfigure}
    \caption{\acl{TTF} versus application lifetime.}\label{fig:lifetimes}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figs/EdgeDroid2ExperimentalSetup.png}
    \caption{%
        Experimental setup used to study the implications of the realistic models of human behavior for \ac{WCA}.
        We deploy containerized instances of the client-server loop running the models on a testbed consisting of \num{10} Raspberry Pi clients connected to a cloudlet over a \acs*{COTS} \acs{IEEE} \num{802.11}b/g access point.
    }\label{fig:expsetup}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{subfigure}[]{\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/new_model/lifetime_testbed.png}
        \caption{%
            Mean application lifetimes per testbed configuration.
            Note that due to the low number of samples, means have been calculated using the geometric instead of arithmetic average. 
            Error bars indicate \SI{95}{\percent} \acp{CI}, calculated using bootstrapping.
        }
    \end{subfigure}
    \par\bigskip
    \begin{subtable}{\columnwidth}
        \centering
        \begin{tabular}{lrrrr}
            \toprule
            \# clients & 1 & 4 & 7 & 10 \\
            \ac{RTT} & \SI{0.42}{\second} & \SI{1.12}{\second} & \SI{1.92}{\second} & \SI{2.68}{\second} \\
            \bottomrule
        \end{tabular}
        \caption{Mean measured \aclp{RTT} for each testbed configuration.}
    \end{subtable}
    \par\bigskip
    \begin{subfigure}[]{\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/new_model/lifetime_testbed_diff.png}
        \caption{%
            Percentage difference in mean application lifetimes with respect to the reference model.
            Confidence intervals have been omitted due to the low number of samples and the use of the geometric mean.
        }
    \end{subfigure}
    \caption{Application lifetimes in the realistic scenarios.}\label{fig:testbed_lifetimes}
\end{figure}

>>>>

\begin{figure}
    \centering
    \begin{subfigure}[]{\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2023EdgeDroid2/figs/new_model/lifetime_all_ttfs.png}
        \caption{%
            Evolution of mean application lifetimes as \acp{TTF} increase.
            Error bars indicate \SI{95}{\percent} \acp{CI}.
        }
    \end{subfigure}
    \begin{subfigure}[]{\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2023EdgeDroid2/figs/new_model/lifetime_diff.png}
        \caption{%
            Percentage difference in mean application lifetimes with respect to the reference model at select \acp{TTF}.
            Error bars indicate the \SI{95}{\percent} \acp{CI}, calculated using a two-sided T-test.
        }
    \end{subfigure}
    \caption{\acl{TTF} versus application lifetime.}\label{fig:lifetimes}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{publications/2023EdgeDroid2/figs/EdgeDroid2ExperimentalSetup.png}
    \caption{%
        Experimental setup used to study the implications of the realistic models of human behavior for \ac{WCA}.
        We deploy containerized instances of the client-server loop running the models on a testbed consisting of \num{10} Raspberry Pi clients connected to a cloudlet over a \acs*{COTS} \acs{IEEE} \num{802.11}b/g access point.
    }\label{fig:expsetup}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{subfigure}[]{\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2023EdgeDroid2/figs/new_model/lifetime_testbed.png}
        \caption{%
            Mean application lifetimes per testbed configuration.
            Note that due to the low number of samples, means have been calculated using the geometric instead of arithmetic average. 
            Error bars indicate \SI{95}{\percent} \acp{CI}, calculated using bootstrapping.
        }
    \end{subfigure}
    \par\bigskip
    \begin{subtable}{\columnwidth}
        \centering
        \begin{tabular}{lrrrr}
            \toprule
            \# clients & 1 & 4 & 7 & 10 \\
            \ac{RTT} & \SI{0.42}{\second} & \SI{1.12}{\second} & \SI{1.92}{\second} & \SI{2.68}{\second} \\
            \bottomrule
        \end{tabular}
        \caption{Mean measured \aclp{RTT} for each testbed configuration.}
    \end{subtable}
    \par\bigskip
    \begin{subfigure}[]{\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2023EdgeDroid2/figs/new_model/lifetime_testbed_diff.png}
        \caption{%
            Percentage difference in mean application lifetimes with respect to the reference model.
            Confidence intervals have been omitted due to the low number of samples and the use of the geometric mean.
        }
    \end{subfigure}
    \caption{Application lifetimes in the realistic scenarios.}\label{fig:testbed_lifetimes}
\end{figure}

### 2022-12-15 implications_optimization.tex
modifications to work with thesis

\begin{figure*}
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/new_model/sampling_optimization.png}
        \caption{%
            Round-trip time versus mean number of captured samples per step, averaged over all \num{100} repetitions of the experiment.
            Note the logarithmic scale on the vertical axis.
            Error bars indicate \SI{95}{\percent} \acp{CI}.
        }
    \end{subfigure}\\
    \medskip
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/new_model/sampling_optimization_diff.png}
        \caption{%
            Percentage difference in mean number of captured samples per step by the sample-count-optimized approach with respect to the three reference schemes.
            In other words, curves represent the relative performance of the sample-count-optimized scheme when using the corresponding reference scheme as baseline.
            Error bars indicate \SI{95}{\percent} \acp{CI}, calculated using a two-sided t-test.
        }
    \end{subfigure}
    \caption{%
        Summary of results for experiment comparing the sample-count-optimized aperiodic sampling scheme to the reference schemes and \textcite{Wang2019Towards}'s \ac{CDF}-based approach.
    }\label{fig:optimization:samples}
\end{figure*}

@@

\begin{figure*}
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/new_model/energy_optimization.png}
        \caption{%
            Round-trip time versus mean per step energy consumption, averaged over all \num{100} repetitions of the experiment.
            Error bars indicate \SI{95}{\percent} \acp{CI}.
        }
    \end{subfigure}\\
    \medskip
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/new_model/energy_optimization_diff.png}
        \caption{%
            Percentage difference in mean per step energy consumption by the energy-optimized sampling scheme with respect to the three reference schemes.
            Error bars indicate \SI{95}{\percent} \acp{CI}, calculated using a two-sided t-test.
        }
    \end{subfigure}
    \caption{%
        Summary of results for experiment comparing the energy-optimized aperiodic sampling scheme to the reference schemes and \textcite{Wang2019Towards}'s \ac{CDF}-based approach.
    }\label{fig:optimization:energy}
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2023EdgeDroid2/figs/new_model/sampling_optimization.png}
        \caption{%
            Round-trip time versus mean number of captured samples per step, averaged over all \num{100} repetitions of the experiment.
            Note the logarithmic scale on the vertical axis.
            Error bars indicate \SI{95}{\percent} \acp{CI}.
        }
    \end{subfigure}\\
    \medskip
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2023EdgeDroid2/figs/new_model/sampling_optimization_diff.png}
        \caption{%
            Percentage difference in mean number of captured samples per step by the sample-count-optimized approach with respect to the three reference schemes.
            In other words, curves represent the relative performance of the sample-count-optimized scheme when using the corresponding reference scheme as baseline.
            Error bars indicate \SI{95}{\percent} \acp{CI}, calculated using a two-sided t-test.
        }
    \end{subfigure}
    \caption{%
        Summary of results for experiment comparing the sample-count-optimized aperiodic sampling scheme to the reference schemes and \textcite{Wang2019Towards}'s \ac{CDF}-based approach.
    }\label{fig:optimization:samples}
\end{figure*}

@@

\begin{figure*}
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2023EdgeDroid2/figs/new_model/energy_optimization.png}
        \caption{%
            Round-trip time versus mean per step energy consumption, averaged over all \num{100} repetitions of the experiment.
            Error bars indicate \SI{95}{\percent} \acp{CI}.
        }
    \end{subfigure}\\
    \medskip
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2023EdgeDroid2/figs/new_model/energy_optimization_diff.png}
        \caption{%
            Percentage difference in mean per step energy consumption by the energy-optimized sampling scheme with respect to the three reference schemes.
            Error bars indicate \SI{95}{\percent} \acp{CI}, calculated using a two-sided t-test.
        }
    \end{subfigure}
    \caption{%
        Summary of results for experiment comparing the energy-optimized aperiodic sampling scheme to the reference schemes and \textcite{Wang2019Towards}'s \ac{CDF}-based approach.
    }\label{fig:optimization:energy}
\end{figure*}

### 2022-12-15 model.tex
modifications to work with thesis

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figs/new_model/ttf_to_exectime.png}
    \caption{%
        Effects of feeding three different \acp{TTF} (\emph{low}, \SI{0}{\second}, \emph{medium}, \SI{2.5}{\second}, or \emph{high}, \SI{5}{\second}) into the model on the generated execution times.
        Higher \acp{TTF} directly lead to higher execution times.
        Error bars indicate the \SI{95}{\percent} \ac{CI}.
    }\label{fig:ttf_to_exectime}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figs/new_model/exectime_over_steps.png}
    \caption{%
    Effects of prolonged exposure to constant levels of system impairment on the model.
    At low (\SI{0}{\second}) \ac{TTF}, the models speed-up over time; conversely at high (\SI{5.0}{\second}) \ac{TTF}, the models either present no change or drastically increase their generated execution times, depending on the level of neuroticism.
    Error bands indicate \SI{95}{\percent} \ac{CI}.
    }\label{fig:exectimeduration}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figs/new_model/transitions.png}
    \caption{%
        Effects of changes in system impairment on subsequently generated execution times.
        These effects linger on after the change, and thus execution times immediately after a transition are either consistently lower or higher than otherwise at the new \ac{TTF}, depending on the old \ac{TTF}.
        Error bars indicate \SI{95}{\percent} \ac{CI}.
    }\label{fig:transitions}
\end{figure*}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{model_data/frame_probabilities.png}
    \caption{%
        Probability density of frame result tags as a step progresses.
        Note that \texttt{SUCCESS} frames are not included as --- by definition --- the probability for success frames is \num{1} for all normalized instant values greater than or equal to \num{1.0}.
    }\label{fig:frameprobs}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{publications/2023EdgeDroid2/figs/new_model/ttf_to_exectime.png}
    \caption{%
        Effects of feeding three different \acp{TTF} (\emph{low}, \SI{0}{\second}, \emph{medium}, \SI{2.5}{\second}, or \emph{high}, \SI{5}{\second}) into the model on the generated execution times.
        Higher \acp{TTF} directly lead to higher execution times.
        Error bars indicate the \SI{95}{\percent} \ac{CI}.
    }\label{fig:ttf_to_exectime}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{publications/2023EdgeDroid2/figs/new_model/exectime_over_steps.png}
    \caption{%
    Effects of prolonged exposure to constant levels of system impairment on the model.
    At low (\SI{0}{\second}) \ac{TTF}, the models speed-up over time; conversely at high (\SI{5.0}{\second}) \ac{TTF}, the models either present no change or drastically increase their generated execution times, depending on the level of neuroticism.
    Error bands indicate \SI{95}{\percent} \ac{CI}.
    }\label{fig:exectimeduration}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{publications/2023EdgeDroid2/figs/new_model/transitions.png}
    \caption{%
        Effects of changes in system impairment on subsequently generated execution times.
        These effects linger on after the change, and thus execution times immediately after a transition are either consistently lower or higher than otherwise at the new \ac{TTF}, depending on the old \ac{TTF}.
        Error bars indicate \SI{95}{\percent} \ac{CI}.
    }\label{fig:transitions}
\end{figure*}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{publications/2023EdgeDroid2/model_data/frame_probabilities.png}
    \caption{%
        Probability density of frame result tags as a step progresses.
        Note that \texttt{SUCCESS} frames are not included as --- by definition --- the probability for success frames is \num{1} for all normalized instant values greater than or equal to \num{1.0}.
    }\label{fig:frameprobs}
\end{figure}
